A Critical Review of Sophistication and Model Selection in Algorithmic Statistics

### 2014-12-02 Facticity/Facticity/paper.tex
Effective complexity

Separately, G\'acs, Tromp and Vit\'anyi \cite{}, built on the idea of the structure function to establish a framework of \emph{algorithmic statistics}, in the hope of founding a statistical theory not on probabilistic notions, but on combinatorical ones. This echoes Kolmogorv's own hope for the theory of information:
\begin{quotation}
\noindent Information theory must precede probability theory and not be based on it. By the very essence of this discipline, the foundations of information theory must have a finite combinatorial character
\end{quotation}

@@

>>>>

Separately, G\'acs, Tromp and Vit\'anyi \cite{}, built on the idea of the structure function to establish a framework of \emph{algorithmic statistics}, in the hope of founding a statistical theory not on probabilistic notions, but on combinatorical ones. This echoes Kolmogorov's own hope for the theory of information:
\begin{quotation}
\noindent Information theory must precede probability theory and not be based on it. By the very essence of this discipline, the foundations of information theory must have a finite combinatorial character
\end{quotation}

@@

\subsection{Effective complexity}

\begin{itemize}
\item Model class is \emph{ensembles}. Equivalent to $\K$.
\item Description method for models is $L(m) = K(m)$ (the minimization is not mentioned explicitly, but we'll give them the benefit of the doubt).
\item The threshold function is equal to the minimum two-part code: $\tau(x)=L^m(x)$.
\item Gell-mann and Lloyd acknowledge that representations exist with small and large models. The choice from the candidate set is made by applying a time-bound to the computation from the string to the model, but not to the decoding of the model itself. The idea is that this forces `deep' information into the model, and shallow information into the data. Presumably, the representation with the smallest model code under this constraint is chosen.   
\end{itemize} 
\pb{We can still manipulate the UTM so that all non-singleton representations are pushed out of the candidate set. Since the model side is allowed unbounded decoding time, this invalidates effective complexity.}
